{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Analysis, Convergence, and Applications }

### 2024-12-17 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

    Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity that is slower than

@@

    Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal. 

@@

    This section swiftly exposes the constructions of the Nesterov's estimating sequence for accelerated proximal gradient method. A similar accelerated projected gradient is Algorithm (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}. 

>>>>

    Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity of function value that is slower than

@@

    Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$ in function value, making it optimal. 

@@

    This section swiftly exposes the constructions of the Nesterov's estimating sequence for accelerated proximal gradient method. A similar accelerated projected gradient is \\ Algorithm (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}. 

### 2024-12-17 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 \in (0, L]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \text{find }&\alpha_k \in (0, 1), \rho_k > 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 < \rho_k \alpha_k^2 < 1, 
            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            g_k &= \mathcal G_L y_k, 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}
    \begin{observation}\label{obs:r-wapg-observation-1}
        If $\alpha_0 \in (0, 1)$ which is true by $\gamma_0 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k > 0$ because: 
            \alpha_k &=
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
            & > 0. 
        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        An upper bound can be identified by using inductive hypothesis and considering: 
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            &<
                \frac{\mu}{L} + 
                \sup_{x \in (0, 1)}
                \left\lbrace
                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                \right\rbrace
            & \le \frac{1}{2}\left(
                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
            \right) \le 1. 
        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        However, the limit of $\alpha_k$ could be 1. 
    \end{observation}

@@

        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 

@@

        Choose $R_0= 0$ to be the base case. 

@@

                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})

@@

                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)

@@

                F(x_0) - F(x^*) + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2

@@

            &\ge R_0 \prod_{i = 0}^{k} \left(1 - \alpha_i\right) = 0. 

@@

        The last equality is by the assumption that $R_0 = 0$. 

@@

                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_t(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is an rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

@@

            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and for all $k\ge 0$ they are algebraically equivalent to

@@

        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
            Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
                \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
                \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}

@@

            Let iterates $(x_k, v_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k, \rho_k)_{k \ge0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge0$, iterate $(v_k)_{k \ge 0}, (x_k)_{k \ge 0}, (y_k)_{k \ge0}$ are algebraically equivalent to: 

@@

    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form}
        Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 

@@

        The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 

@@

            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
            \alpha_k &= 
            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}

@@

@@

            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 

@@

    \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
        \;\\
        Let sequence $(\alpha_k, \rho_k)_{k \ge0}$ and iterates $(x_k, v_k, y_k)_{k\ge 0}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
        Then the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}

@@

    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
        Initialize any $\alpha_0 \in (0, 1)$. 
        The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 
        \begin{align*}
            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
            \\
            \alpha_k &= 
            \frac{1}{2}\left(
            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
            +
            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right), 
            \\
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
        $$
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
        = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
        $$

>>>>

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$ or equivalently: $(x_1, y_1), (y_1, v_1)$. 
        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 1$: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
                \\
                \gamma_1 & k = 1. 
            \end{cases}\right\rbrace,
            \\
            \text{find }&\alpha_k \in (0, 1), \rho_k > 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 < \rho_k \alpha_k^2 < 1, 
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
        The initial condition is generic so it can describe accelerated proximal gradient method in the middle of its executions. 
        \par
        We only need any two of the intertes among $x_1, y_1, v_1$ because we can solve 
        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$ given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$. 
        \par
        % Usually, people initialize the method with one step of gradient descent. 
        % For example, given any $y_0 = x_{0} = v_0\in \RR^n$, we can choose the initial condition $(x_1, v_1)$ to be $v_1 = x_1 = T_L y_{0}$,

    \end{observation}
    \begin{observation}\label{obs:r-wapg-observation-1}
        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right). 
        \end{align*}
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k > 0$ because: 
        \begin{align*}
            \alpha_k &=
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &\ge 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
            \\
            & > 0. 
        \end{align*}
        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        An upper bound can be identified by using inductive hypothesis and considering: 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &<
            \frac{1}{2}\left(
                \frac{\mu}{L} + 
                \sup_{x \in (0, 1)}
                \left\lbrace
                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                \right\rbrace
            \right)
            \\
            & \le \frac{1}{2}\left(
                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
            \right) \le 1. 
        \end{align*}
        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        However, the limit of $\alpha_k$ could be 1. 
    \end{observation}

@@

        Let vectors $(x_k, y_k, v_k)_{k \ge 1}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 

@@

        Choose $R_1= 0$ to be the base case. 

@@

                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})

@@

                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)

@@

                F(x_1) - F(x^*) + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

                F(x_1) - F^* + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

            &\ge R_1 \prod_{i = 1}^{k} \left(1 - \alpha_i\right) = 0. 

@@

        The last equality is by the assumption that $R_1 = 0$. 

@@

                F(x_1) - F^* + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_k, y_k, x_{k + 1}, z_{k + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_k(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

@@

            Choose any $\gamma_1 \in (0, L]$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to

@@

        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
            Given any initial $\alpha_1 \in (0, 1)$, $(x_1, y_1)$ or equivalently $(x_1, v_1), (y_1, v_1)$. 
            Assume $\mu < L$. 
            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge 1}$ by the procedures: 
            \begin{align*}
                & y_k = 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                & x_{k + 1} = 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                & v_{k + 1} = 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
                \\
                & \text{choose any } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
                \\
                & \alpha_{k + 1} = 
                \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
                +
                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
                \right). 
            \end{align*}
        \end{definition}

@@

            Let iterates $(x_k, v_k, y_k)_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge 1$, iterate $(v_k)_{k \ge 1}, (x_k)_{k \ge 1}, (y_k)_{k \ge1}$ are algebraically equivalent to: 

@@

    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
        Given any initial $\alpha_1 \in (0, 1)$, $(x_1, v_1)$. 

@@

        The algorithm generates sequences of vector iterates $(x_k, v_k, y_k)_{k \ge 2}$ by the procedures: 

@@

            & y_k = 

@@

            & x_{k + 1} = 

@@

            & v_{k + 1} = 
            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k), 
            & \text{choose any }   \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
            &\alpha_{k + 1} = 
            \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
            \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}

@@

    \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
        \;\\
        Let sequence $(\alpha_k, \rho_k)_{k \ge 1}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
        Then for all $k \ge 1$, the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}

@@

    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
        Initialize any $\alpha_1 \in (0, 1)$. 
        The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 
        \begin{align*}
            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
            \\
            \alpha_k &= 
            \frac{1}{2}\left(
            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
            +
            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right), 
            \\
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
        $$
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
        = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
        $$

### 2024-12-17 Notebook LaTEX/Proposal/main.tex
>w<, changes

\begin{abstract} 
    \noindent
    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our method of spectral momentum. 
    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
    We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegetation covers.

@@

\tableofcontents

>>>>

\begin{abstract} 
    \noindent
    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our method of spectral momentum. 
    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
    Furthermore, we present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data analytics by extract spectral signatures of ground vegetation covers.

@@

\newpage
\tableofcontents
